a and generators

### 2022-04-23 documentos/intro.tex
Rev_App

Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195, PhysRevLett.126.170404,Ollivier2001}, including
entanglement~\cite{Horodecki}, are an important
resource for a wide variate of tasks that include teleportation~\cite{PhysRevLett.70.1895},
quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
for multi-particle systems~\cite{Horodecki},  and important part
of the efforts of the community implementing quantum technologies is 
devoted to tackle this issue from an experimental \cite{Mooney_2021,Briegel1998} and
theoretical \cite{Bennett1996,Georgescu2020,RevModPhys.87.307} point of view. 
The process by which quantum correlations are unintentionally dissipated
is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
One of the main tools to study the effects of decoherence are 
quantum channels. Quantum channels can describe quantum
noise~\cite{davalosdivisibility,ruskai}, open quantum systems
dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
graining~\cite{Duarte2017,pinedacg}. 
%
% The identification of families of quantum channels among the whole convex set
% of quantum channels associated to a Hilbert space, is crucial to understand
% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
% graining~\cite{Duarte2017,pinedacg}. 
One of the main difficulties to characterize quantum channels is that,
similar to quantum states, the parameters needed to describe them
increases overwhelmingly rapidly with the dimension of the Hilbert space.
%
Moreover, such parameters are constrained in a complicated way by 
physical conditions, such as complete positivity ~\cite{zimansbook}.
% Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.
% 
% \cpnote{quiza quitar (QQ), o modificiar 
% a decir que el numero de parametros crece exponencialmente con el numero 
% de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
% qubit case is difficult to
% analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
% the displacement vector and $3$ describing the compression of the Bloch
% sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. 
Describing in detail families of channels having a given property provides
insight into the jungle of quantum operations.
For the qubit case there are several studies concerning the unital case, for which
non-trivial properties can be described using only $3$ parameters, which in
turn form the well known tetrahedron of Pauli
channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
% For general
% finite-dimensional channels, several families of channels have been defined.
More generally, in~Ref.~\cite{nathanson2007pauli} the authors study families of 
convex combinations of quantum-classical channels that relate to
% have a close relation with 
unital qubit channels with positive eigenvalues, and give a
generalization of the Bloch sphere. 
% {\blue We will show later that some of the channels studied here are also
% quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada
% mejor en tanto a la escritura. Propongo omitirla, despues se volvera a
% mencionar esto pero en donde corresponde.}
Similarly, a generalization of Pauli channels based on mutually unbiased
measurements is introduced and studied in Ref.~\cite{Siudzinska2020}. Other
studies of channels beyond the qubit can be
found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
% \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
% mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
% discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}

\par
In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices), the resulting maps are unital and diagonal in the Pauli strings'
basis.
Moreover, these channels describe decoherence in a similar way as the aforementioned
single-qubit channels describe decoherence. \cpnote{Si alguien mejora esta
frase, de lujo}
We call such maps \textit{Pauli component erasing} (\pce{}) maps . We
derive necessary and sufficient conditions for such mappings to be completely
positive trace preserving, thus, showing which idempotent operations are valid
quantum channels (\pce{} channels). Additionally, we characterize the algebraic
properties of the set of \pce{} channels, showing that is equipped with a
semigroup structure, which is later used to derive physical implementations.
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. In
section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize completely positive maps by interpreting
\pce{} maps as finite vector spaces. In section~\ref{sec:generators} we study
generators of the semigroup structure of the set of \pce{} channels, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.
%
To finish, we conclude in section~\ref{sec:conclusions}.
% }}}

>>>>

Quantum correlations~\cite{PhysicsPhysiqueFizika.1.195, PhysRevLett.126.170404,Ollivier2001}, including
entanglement~\cite{Horodecki}, are an important
resource for a wide variate \afnote{(variety)} of tasks that include teleportation~\cite{PhysRevLett.70.1895},
quantum computation~\cite{nielsen_chuang_2011}, and others~\cite{Sapienza2019}.
However, this resource is also extremely delicate~\cite{nielsen_chuang_2011,Schlosshauer2004}, specially 
for multi-particle systems~\cite{Horodecki},  and important part
of the efforts of the community implementing quantum technologies is 
devoted to tackle this issue from an experimental \cite{Mooney_2021,Briegel1998} and
theoretical \cite{Bennett1996,Georgescu2020,RevModPhys.87.307} point of view. 
The process by which quantum correlations are unintentionally dissipated
is called decoherence~\cite{Schlosshauer2004,sep-qm-decoherence}.
One of the main tools to study the effects of decoherence are 
quantum channels. Quantum channels can describe quantum
noise~\cite{davalosdivisibility,ruskai}, open quantum systems
dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
graining~\cite{Duarte2017,pinedacg}. 
%
% The identification of families of quantum channels among the whole convex set
% of quantum channels associated to a Hilbert space, is crucial to understand
% quantum noise~\cite{davalosdivisibility,ruskai}, open quantum systems
% dynamics~\cite{nielsen_chuang_2011,breuerbook}, and recently even coarse
% graining~\cite{Duarte2017,pinedacg}. 
One of the main difficulties to characterize quantum channels is that,
similar to quantum states, the parameters needed to describe them
increases overwhelmingly rapidly with the dimension of the Hilbert space.
%
Moreover, such parameters are constrained in a complicated way by 
physical conditions, such as complete positivity ~\cite{zimansbook}.
% Such parameters are not fully independent, the complete positivity condition imposes the regions that have physical meaning~\cite{zimansbook}.
% 
% \cpnote{quiza quitar (QQ), o modificiar 
% a decir que el numero de parametros crece exponencialmente con el numero 
% de particulas.}\ddnote{Atendido, dejo lo esencial y relacionado con el articulo}. Therefore, even the
% qubit case is difficult to
% analyze having $12$ parameters corresponding to $6$ angles, $3$ components of
% the displacement vector and $3$ describing the compression of the Bloch
% sphere~\cite{ruskai}\cpnote{QQ}\ddnote{quitemoslo}. 
Describing in detail families of channels having a given property provides
insight into the jungle of quantum operations.
For the qubit case there are several studies concerning the unital case, for which
non-trivial properties can be described using only $3$ parameters, which in
turn form the well known tetrahedron of Pauli
channels~\cite{Rybar2012,ruskai,davalosdivisibility}. 
% For general
% finite-dimensional channels, several families of channels have been defined.
More generally, in~Ref.~\cite{nathanson2007pauli} the authors study families of 
convex combinations of quantum-classical channels that relate to
% have a close relation with 
unital qubit channels with positive eigenvalues, and give a
generalization of the Bloch sphere \afnote{seria bueno mencionar en que sentido es dicha generalización.}. 
% {\blue We will show later that some of the channels studied here are also
% quantum-classical.}\ddnote{Esta frase no me gusta, pero no se me occure nada
% mejor en tanto a la escritura. Propongo omitirla, despues se volvera a
% mencionar esto pero en donde corresponde.}
Similarly, a generalization of Pauli channels based on mutually unbiased
measurements is introduced and studied in Ref.~\cite{Siudzinska2020}. Other
studies of channels beyond the qubit can be
found~\cite{pub.1117408526,pub.1060516327,pub.1014660854}.
% \cpnote{Me gusta la idea de ir sobre un par de familias, pero no veo para que 
% mencionar a las MUBs aca, ni paraque introducir la sigla. Ojala podamos 
% discutir que familias mencionamos acá}\ddnote{atendido como fue acordado en la reunion :)}

\par
In this work we present a generalization of idempotent Pauli channels, \ie{}
the qubit flip operations (bit, phase and bit-phase when the flip probability is $1/2$), total depolarizing qubit
channel and the identity channel, to the case of $N$ qubits. 
% \cpnote{Mencionar decoherencia} 
The generalization is done by extending
Pauli observables to \textit{Pauli strings} (tensor products of Pauli
matrices), the resulting maps are unital and diagonal in the Pauli strings'
basis.
Moreover, these channels describe decoherence in a similar way as the aforementioned
single-qubit channels describe decoherence. \cpnote{Si alguien mejora esta
frase, de lujo}
\afnote{In addition, these channels describe the decoherence process in a similar way as the aforementioned
ones for the single-qubit case.}
We call such maps \textit{Pauli component erasing} (\pce{}) maps \afnote{From now on we refer to them as \textit{Pauli component erasing} (\pce{}) maps}. We
derive necessary and sufficient conditions for such mappings to be completely
positive trace preserving \afnote{(CPTP)}, thus, showing which idempotent operations are valid
quantum channels (\pce{} channels). Additionally, we characterize the algebraic
properties of the set of \pce{} channels, showing that \afnote{it} is equipped with a
semigroup structure, which is later used to derive physical implementations.
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we recall
the properties of quantum channels needed to proceed with the definition 
of 
% the tools to unders
% refreshing of quantum channels theory and the definition of 
\pce{} maps. In
section~\ref{sec:math} we diagonalize analytically the Choi matrix for
arbitrary \pce{} maps and characterize completely positive maps by interpreting
\pce{} maps as finite vector spaces \afnote{The section~\ref{sec:math} is devoted to present an analytical diagonalization of the the Choi matrix for
arbitrary \pce{} maps, and to provide a characterization of completely positive maps by interpreting
\pce{} maps as finite vector spaces}. In section~\ref{sec:generators} we study
generators of the semigroup structure of the set of \pce{} channels, and use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.
%
\afnote{We study the
generators of the semigroup structure associated to the set of \pce{} channels in section~\ref{sec:generators}, and we use
them to derive meaningful physical interpretations of \pce{} channels in
section~\ref{sec:kraus}, as well Kraus operators of the generators.}
% 
\afnote{No entendí que se quiere decir con ``as well Kraus operators of the generators"} To finish, we conclude in section~\ref{sec:conclusions}.
% }}}

### 2022-04-23 documentos/kraus.tex
Rev_App

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics. Moreover, these processes lead to a monotonically lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically decreasing of the determinant, see Ref.~\cite{cirac}).
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove what in fact they are, and
give two examples of Markovian implementations.
%
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model.

@@

% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs \janote{introducimos esta notación antes?} and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEGs leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$ \janote{$r_0$ and $r_\alpha$}
invariant~\cite{nielsen_chuang_2011}. \ddnote{agrego lo de los flips aqui}{\blue Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$. In fact, tracing out all particles except particle $k$ gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}). And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel.}

We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce \janote{are indeed} a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$, see~\Eref{eq:1},
% \label{}
% \end{equation}
which in turn imply that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on a $N$-qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}.
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by Kraus operators  \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the channel is a PCEG.

@@

% \cpnote{We might have spoken about the notation of the generators and here we 
% can add a sentence about it, but I will wait till JA writes his part.}
% Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
% generator. This notation is based on the action on each individual qubit. (ii) Counting the
% number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
% from other arguments. 
% }}}
\subsection{Pure dissipative implementation} % {{{
% {\red [viejo] Any PCE channel can be seen as the fixed point of some
% decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos
% los canales son resultado de lindblad.}
In this section we show that any PCE channel can be seen as the
fixed point of some decoherence process, starting with PCEGs and 
then generalizing to more general channels. 
% Me gustaria modificar esta
% frase para que pueda ser apreciada mejor} \ddnote{la modificacion fue leve
% debido a que la mayor parte del contenido esta en la introduccion de la
% seccion}. 
% We start with PCEGs. 
Consider the following dynamical process that
implements $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
\end{align}
where $\gamma>0$. It is easy to show that the family of channels $\mcG_{\vec
\alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup,
\ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha,
t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
time-homogeneous Markovian process, those are always characterized by some
Lindblad generator~\cite{lindblad}. The Lindblad generator of $\mcG_{\vec
\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with the standard
procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio
$\gamma/2$ is simply $\sigma_{\vec \alpha}$. Notice that $\sigma_{\vec \alpha}$
is trace-less, therefore the process is pure dissipative~\cite{cirac}.

@@

% }}}
\subsection{Collision model implementation} % {{{
We show now that PCE channels can also be implemented with \textit{simple
collision models}~\cite{Ziman2010}. To do this, observe that using the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
be implemented using an unitary over the system and an
ancilla. Since PCEG
always have Kraus rank $2$, one can
always choose a qubit as the ancillary system. Concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]=
    \tr_{\text{qubit}} \left( 
         U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U_{\vec \alpha}^\dagger{} 
     \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
the unitary defined as follows,
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}= \frac{1}{\sqrt{2}} 
   \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}=\frac{1}{\sqrt{2}} 
   \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model
with as many collisions as generators needed. In fact, generators are described
with one collision. For the general case consider some PCE channel $\mcE$
generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots,
\mcG_{\vec \alpha_M} \right\}$. For this we can define an environment
consisting of $M$ qubits initially in the state $\left( \projj{0}
\right)^{\otimes M}$, or equivalently one qubit with the additional assumption
that its state is reset to $\ket{0}$ after each collision (memory-less
collisions). The collision with the $k\text{th}$ particle is described by
$U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$
particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left[ \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right) \rho \otimes \left(\projj{0}\right)^{\otimes M} \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right],
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits. Notice that as PCEGs commute, the order of the collisions can be any.
% \begin{itemize}
% \item Relate to decoherence, for PCEG\ddnote{hecho}
% \item Play with non PCEG PCEs\ddnote{hecho}
% \item Dependiendo de si sale algo bonito, podemos poner algun modelo en
% particular para todos los canales (sistema central + ambiente). Seria de buscar
% dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
% \todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
% \end{itemize} 
% 
% \begin{equation}
% \mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
% \label{eq:Nqubit_semigroup}
% \end{equation}

>>>>

Lindblad processes arise naturally in many theoretical~\cite{lindblad,kossa,kossa2,Gorini1976,cirac,davalosdivisibility} and
experimental~\cite{PhysRevA.67.042322} settings and are archetypical in decoherence dynamics. Moreover, these processes lead to a monotonically \afnote{monotonic (continuous)} lose of information~\cite{breuerreview} and describe non invertible channels in the asymptotic limit $t\to \infty$ (this can be seen from the monotonically \afnote{(continuous)} decreasing of the determinant, see Ref.~\cite{cirac}).
It is known that not every quantum channel can be seen as a snapshot of a
process
arising from a traditional Lindblad equation or even a time-dependent Lindblad
equation~\cite{cirac,davalosdivisibility}. 
Therefore, an interesting question is whether \pce{} channels can be seen as limit points of
some Markovian processes. In this section we prove what \afnote{that} in fact they are, and
give two examples of Markovian implementations.
%
The first
one consist in identifying each \pce{} channel as a fixed point of some pure
dissipative process. The second, in identifying each \pce{} channel as fixed
points of some memory-less collision model \afnote{The first of them consists in identifying each \pce{} channel as a fixed point of some pure dissipative process, and in the second implementation we relate each \pce{} channel to fixed
points of some memory-less collision model }.

@@

% }}}
\subsection{Kraus representation} % {{{
To derive the aforementioned implementations, we exploit the existence of the
PCEGs \janote{introducimos esta notación antes?} \afnote{(acabo de colocarla en el 3er parrafo de la sección de generadores)} and their \textit{Kraus representation} (or operator-sum representation)
which, for an arbitrary channel $\mcE$,  reads 
\begin{equation}
\mcE[\rho]=\sum_i K_i \rho
K_i^\dagger{},
\end{equation}
with $\sum_i K_i^\dagger{}K_i=\one$ (the trace-preserving condition)~\cite{Kraus1983}.
% The Kraus operators corresponding to one single qubit PCEs are 
% $\{\openone/\sqrt2, \sigma_i/\sqrt2\}$,
% % \begin{equation}
% % \{\openone/\sqrt2, \sigma_i/\sqrt2\}
% % \label{eq:kraus:PCE}
% % \end{equation}
% corresponding to the operation that leaves the component $\sigma_i$
% invariant~\cite{nielsen_chuang_2011}.
Inspection of the Kraus operators of two qubit PCEGs leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are 
\afnote{By inspection, it is easy to prove that two qubit PCEGs leads to
the ansatz that the Kraus operators for the generator of 
$\mcG_{\vec \alpha}$ are}
\begin{equation}
K_0=\frac{\openone}{\sqrt2}, \quad K_1=\frac{\sigma_{\vec \alpha}}{\sqrt2},
% \left\{\openone/\sqrt2, 
% \left(\bigotimes_{k=1}^N \sigma_{\alpha_k}\right)/\sqrt2\right\}. 
\label{eq:kraus:PCE}
\end{equation}
since the Kraus operators corresponding to one \afnote{a} single qubit PCEs are 
$\{\openone/\sqrt2, \sigma_\alpha/\sqrt2\}$,
corresponding to the operation that leaves the component $\sigma_\alpha$ \janote{$r_0$ and $r_\alpha$}
invariant~\cite{nielsen_chuang_2011}. \ddnote{agrego lo de los flips aqui}{\blue Notice that according to Kraus operators, the generators $\mcG_{\vec \alpha}$ are $N$-qubit flip channels with flip probability of $1/2$, where the joint flip is $\rho \mapsto \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}$. In fact, tracing out all particles except particle $k$ \afnote{...except the $k-$th one} gives the well known qubit flip channels, \ie{} $\tr_{\not k} \mcG_\valpha=\mcG_{\alpha_k}$ (see~ \eref{eq:generator:individual:qubit}). And more generally, tracing out $m$ particles leaves a $N-m$ particles flip channel \afnote{with weight $1/2$}.}

We shall first show that the Kraus operators in \eref{eq:kraus:PCE} produce \janote{are indeed} a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$, see~\Eref{eq:1},
% \label{}
% \end{equation}
which in turn imply \afnote{implies} that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on a $N$-qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}.
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by \afnote{the} Kraus operators \janote{in} \eref{eq:kraus:PCE} is a PCE channel. Moreover, one can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the channel is a PCEG.

@@

% \cpnote{We might have spoken about the notation of the generators and here we 
% can add a sentence about it, but I will wait till JA writes his part.}
% Two remarks. (i) The notation that we develop with Jose Alfredo coincides with the 
% generator. This notation is based on the action on each individual qubit. (ii) Counting the
% number of generators here is trivial. It is simply $4^n-1$ as previously noticed 
% from other arguments. 
% }}}
\subsection{Pure dissipative implementation} % {{{
% {\red [viejo] Any PCE channel can be seen as the fixed point of some
% decoherence process\cpnote{esto suena obvio, pero no lo es. Es decir no todos
% los canales son resultado de lindblad.}
In this section we show that any PCE channel can be seen as the
fixed point of some decoherence process, starting with PCEGs and 
then generalizing \afnote{extending} to more general channels. 
% Me gustaria modificar esta
% frase para que pueda ser apreciada mejor} \ddnote{la modificacion fue leve
% debido a que la mayor parte del contenido esta en la introduccion de la
% seccion}. 
% We start with PCEGs. 
Consider the following dynamical process that
implements $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
\end{align}
where $\gamma>0$. It is easy to show that the family of channels $\mcG_{\vec
\alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup,
\ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha,
t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative
time-homogeneous Markovian process, those are always characterized by some
Lindblad generator~\cite{lindblad} \afnote{Me parece que se podría conectar mejor esta última frase (pero no pude XD)}. The Lindblad generator of $\mcG_{\vec
\alpha, t}$, denoted by $\mcL_{\vec \alpha}$, can be obtained with \afnote{by} the standard
procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio
$\gamma/2$ is simply $\sigma_{\vec \alpha}$. Notice that $\sigma_{\vec \alpha}$
is trace-less, therefore the process is pure dissipative~\cite{cirac}.

@@

% }}}
\subsection{Collision model implementation} % {{{
We show now that PCE channels can also be implemented with \textit{simple
collision models}~\cite{Ziman2010}. To do this, observe that using \afnote{by employing} the Stinespring dilation theorem~\cite{Stinespring2006}, PCEGs can
be implemented using an unitary over the system and an
ancilla. Since PCEG
always have Kraus rank $2$, one can
always choose a qubit as the ancillary system. Concretely,
\begin{equation}
\mcG_{\vec \alpha}[\rho]=
    \tr_{\text{qubit}} \left( 
         U_{\vec \alpha} \left(\rho\otimes \projj{0}\right) U_{\vec \alpha}^\dagger{} 
     \right),
\end{equation}
where $\tr_{\text{qubit}}$ denotes partial trace over the ancillary qubit, with
the unitary defined as follows,
\begin{align}
U_{\vec\alpha}\ket{\psi} \ket{0}= \frac{1}{\sqrt{2}} 
   \left( \ket{\psi} \ket{0}+\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right),\\
U_{\vec\alpha}\ket{\psi} \ket{1}=\frac{1}{\sqrt{2}} 
   \left( \ket{\psi} \ket{0}-\sigma_{\vec\alpha} \ket{\psi}\ket{1} \right).
\label{eq:Nqubit_stinespring}
\end{align}
Therefore, any concatenation of PCEGs can be described as a collision model
with as many collisions as generators needed. In fact, generators are described
with one collision. For the general case consider some PCE channel $\mcE$
generated with $\left\{ \mcG_{\vec \alpha_1}, \mcG_{\vec \alpha_2}, \dots,
\mcG_{\vec \alpha_M} \right\}$. For this we can define an environment
consisting of \afnote{on} $M$ qubits initially in the state $\left( \projj{0}
\right)^{\otimes M}$, or equivalently one qubit with the additional assumption
that its state is reset to $\ket{0}$ after each collision (memory-less
collisions). The collision with the $k\text{th}$ \afnote{$k\text{-th}$} particle is described by
$U_{\vec \alpha_k}$, which acts solely over the system and the $k\text{th}$
particle. Therefore $\mcE$ can be written as follows,
\begin{equation}
\mcE[\rho]=\tr_{\text{E}} \left[ \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M}\right) \rho \otimes \left(\projj{0}\right)^{\otimes M} \left(U_{\vec \alpha_1} \dots U_{\vec \alpha_M} \right)^\dagger{} \right],
\end{equation}
where $\tr_{\text{E}}$ is the partial trace over the total of the ancillary qubits \afnote{over the whole ancillary qubits}. Notice that as PCEGs commute, the order of the collisions can be any \afnote{the order of the collisions is irrelevant}.
% \begin{itemize}
% \item Relate to decoherence, for PCEG\ddnote{hecho}
% \item Play with non PCEG PCEs\ddnote{hecho}
% \item Dependiendo de si sale algo bonito, podemos poner algun modelo en
% particular para todos los canales (sistema central + ambiente). Seria de buscar
% dilataciones sencillas y razonables por lo menos a los canales generadores.\ddnote{hecho, es el asunto de collision models}
% \todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
% \end{itemize} 
% 
% \begin{equation}
% \mcL_{\vec \alpha}[\Delta]:= \frac{\gamma}{2}\left( \sigma_{\vec\alpha} \Delta \sigma_{\vec\alpha} -\Delta \right).
% \label{eq:Nqubit_semigroup}
% \end{equation}
